---
title: "EDA_NY_taxi"
author: "Team 7"
date: "December 3, 2016"
output:
  html_notebook: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)
library(pbapply)
library(gbm)
library(leaflet)

```

```{r}
date.start <- min(green.smpl.cls.dat$pickup_date)
date.end <- max(green.smpl.cls.dat$pickup_date)
```

# Database: Green taxi rides

## General Properties of the Database

Total Rides: `r nrow(green.smpl.cls.dat)`

Date Start: `r date.start`

Date End: `r date.end`

Total Days: `r date.end - date.start + 1`

Detailed Stats:

```{r}
summary(green.smpl.cls.dat)
```


```{r, fig.width=10, echo=FALSE}
daily.rides <- green.smpl.cls.dat %>% 
  group_by(pickup_date) %>%
  summarise(count.rides = n())

p <- plot_ly(data = daily.rides, 
             x = ~pickup_date,
             y = ~count.rides,
             type = 'scatter',
             mode = 'lines') %>%
  layout(title = "Count of rides per day")
p
```

* There is regularity in the # of rides per day (weekends have more rides?)
* For some reason there are less rides around Jan 23rd


## Basic association rule

* The following histogram shows the most popular rides.
* Ride is defined as (origin,destination)
* The locations are geographically clustered.

```{r, echo=FALSE, fig.width=10}
# Create a column that combines origin,destination

green.smpl.cls.dat$ride <- paste0(green.smpl.cls.dat$pickup_region,
                                  '-',
                                  green.smpl.cls.dat$dropoff_region)


histogram.rides <- green.smpl.cls.dat %>% 
  group_by(ride) %>%
  summarise(count.rides = n())

histogram.rides <- histogram.rides[order(histogram.rides$count.rides, decreasing = TRUE),]
histogram.rides$ride <- factor(histogram.rides$ride, levels = histogram.rides$ride)

p <- plot_ly(data = histogram.rides[1:1000,], 
             x = ~ride,
             y = ~count.rides,
             type = 'bar') %>%
  layout(title = "Rides by popularity")
p
```

```{r}
head(histogram.rides, 20)
```


